An optimization of bidirectional update language based on the idea of reversible computing \thanks{Supported by organization x.}

### 2019-09-05 paper/main.tex
update tex 0509-1439

The first 4 test cases simply use $n$ compose operators to make a composition of $n + 1$ similar $BX$ programs which are non-recursive. For example, \textit{lassoc-comp-replace} looks like $(\ldots((Replace \circ Replace) \circ Replace) \circ \ldots \circ Replace) \circ Replace$, while \textit{rassoc-comp-replace} is like $Replace \circ (Replace \circ (Replace \circ \ldots \circ (Replace \circ Replace)\ldots))$, where there are $n + 1 \ Replace$s in each case. \textit{lassoc-comp-phead} and \textit{rassoc-comp-phead} are similar to the above two. While $Replace$ is a primitive BX program, $phead$ is a combination of such programs. The following is the definition of $phead$ in BiGUL [?]:

We also provide the same $phead$ program in our OCaml system. It rearranges the source, a non-empty list, to a pair of its head element $s$ and its tail $ss$, and the view to a pair $(v, ())$, then we can use $v$ to replace $s$ and $()$ to keep $ss$. $\putbx{phead}{s_0}{v_0}$ returns a list whose head is $v_0$ and tail is the tail of $s_0$. $\getbx{phead}{s_0}$ returns the head of $s_0$. For instance, $\putbx{phead}{[1,2,3]}{100} = [100,2,3]$ and $\getbx{phead}{[1,2,3]} = 1$. If we wanna update the head element of the head element of a list of lists by using the view, we can define a composition like $phead \circ phead$. For example:

    \tab $\putbx{phead \circ phead}{[[1,2,3],[\ ],[4,5]]}{100} = [[100,2,3],[\ ],[4,5]]$\\
    \tab $\getbx{phead \circ phead}{[[1,2,3],[\ ],[4,5]]} = 1$

Similarly, we can use the view to update head element in the nested lists with a composition of a specific number of $phead$s. For both \textit{lassoc-comp-phead} and \textit{rassoc-comp-phead}, we choose input view $v_0$ is 100 and input source $s_0$ is one of the smallest nested lists which make $put$ and $get$ direction on the composition valid.\\

>>>>

The first 4 test cases simply use $n$ compose operators to make a composition of $n + 1$ similar $BX$ programs which are non-recursive. For example, \textit{lassoc-comp-replace} looks like $(\ldots((Replace \circ Replace) \circ Replace) \circ \ldots \circ Replace) \circ Replace$, while \textit{rassoc-comp-replace} is like $Replace \circ (Replace \circ (Replace \circ \ldots \circ (Replace \circ Replace)\ldots))$, where there are $n + 1 \ Replace$s in each case. \textit{lassoc-comp-phead} and \textit{rassoc-comp-phead} are similar to the above two.

In section 5, we defined a composition $phead \circ phead$ for updating the head element of the head element of a list of lists by using the view. Similarly, we can use the view to update head element in the nested lists with a composition of a specific number of $phead$s. For both \textit{lassoc-comp-phead} and \textit{rassoc-comp-phead}, we choose input view $v_0$ is 100 and input source $s_0$ is one of the smallest nested lists which make $put$ and $get$ direction on the composition valid.\\
